---
title: 'Preregistration Form: Analysis Plan'
author: "Caspar J. van Lissa"
date: "`r format(Sys.Date(), '%d %b %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```



# 1.	Title

Many Analysts Replication Project

# 2.	Analysis Team 

```{r}
knitr::kable(data.frame(Surname = "Van Lissa", 
                        Name = "Caspar J.",
                        Affiliation = "Utrecht University",
                        `Email-address` = "c.j.vanlissa@uu.nl"))
```

<!-- (N=10,535 from 24 countries). --> 
		
# 3.	Research Question


## a.	Do religious people have higher well-being?

## b.	Does the relationship between religiosity and well-being depend on perceived cultural norms of religion?

# 4.	Hypotheses

List specific, concise, and testable hypotheses. Please state if the hypotheses are directional or non-directional. If directional, state the direction. A predicted effect is also appropriate here. If a specific interaction or moderation is important to your research, you can list that as a separate hypothesis.

Example
If taste affects preference, then mean preference indices will be higher with higher concentrations of sugar.


# 5.	Variables 

## a.	Dependent variable(s)
State which key dependent variable(s) you will use in your analysis. Name the specific column names of these variables as stated in the data documentation.




## b.	Predictor variable(s)
State which predictor variable (including moderators and covariates) you will use in your analysis. Name the specific column names of these variables as stated in the data documentation.





## c.	Indices
If applicable, please define how measures will be combined into an index (or even a mean) and what measures will be used. Include either a formula or a precise description of the method. If you are using a more complicated statistical method to combine measures (e.g. a factor analysis), please note that here but describe the exact method in the analysis plan section.

Example
We will take the mean of the two questions above to create a single measure of ‘brownie enjoyment.’




# 6.	Analysis Plan 

## a.	Statistical models

What statistical model will you use to test each hypothesis? Please include the type of model (e.g. ANOVA, RMANOVA, MANOVA, multiple regression, SEM, etc) and the specification of the model. This includes each variable that will be included, all interactions, subgroup analyses, pairwise or complex contrasts, and any follow-up tests from omnibus tests. Provide enough detail so that another person could run the same analysis with the information provided. Remember that in your final article any test not included here must be noted as exploratory and that you must report the results of all tests.

Note: This is perhaps the most important and most complicated question within the preregistration. Ask yourself: is enough detail provided to run the same analysis again with the information provided by the user? Be aware for instances where the statistical models appear specific, but actually leave openings for the precise test.

Example
We will use a  2 X 3 repeated measures ANOVA (RMANOVA) with the mean preference indices as the outcome variable and the factors “sweetness” and “color” within subjects to analyze our results. 





## b.	Transformations
If you plan on transforming, centering, recoding the data, or requiring a coding scheme for categorical variables, please describe that process.

Example
The “Effect of sugar on brownie tastiness” does not require any additional transformations. However, if it were using a regression analysis and each level of sweet had been categorically described (e.g. not sweet, somewhat sweet, sweet, and very sweet), ‘sweet’ could be dummy coded with ‘not sweet’ as the reference category.  If any categorical predictors are included in a regression, indicate how those variables will be coded (e.g. dummy coding, summation coding, etc.) and what the reference category will be.





## c.	Inference criteria
What criteria will you use to make inferences? Please describe the information you’ll use (e.g. specify the p-values, Bayes factors, specific model fit indices), as well as cut-off criterion, where appropriate. Will you be using one or two tailed tests for each of your analyses? If you are comparing multiple conditions or testing multiple hypotheses, will you account for this?

Example
We will use the standard p<.05 criteria for determining if the ANOVA and the post hoc test suggest that the results are significantly different from those expected if the null hypothesis were correct. The post-hoc Tukey-Kramer test adjusts for multiple comparisons.





## d.	Data exclusion
How will you determine which data points or samples if any to exclude from your analyses, for instance, based on the attention check or missing data? How will outliers be handled? 

Example
We will verify that each subject answered each of the three tastiness indices. Outliers will be included in the analysis.





## e.	Missing data
How will you deal with incomplete or missing data? 
Note: For the well-being and religiosity measures there are no missing data. See the data documentation for a more detailed overview of missing data for each variable.

Example
If a subject does not complete any of the three indices of tastiness, that subject will not be included in the analysis.




# 7.	Other
If there is any additional information that you feel needs to be included in your preregistration, please enter it here. Literature cited, disclosures of any related work such as replications or work that uses the same data, or other helpful context would be appropriate here.






